Dissertation Proposal

### 2023-11-03 proposal.tex
format file
save new tutorials

\usepackage[switch]{lineno}
\usepackage{xcolor}
\renewcommand\thelinenumber{\textcolor{red}{\arabic{linenumber}}}

\usepackage[utf8]{inputenc} % Use UTF-8 encoding
\usepackage[T1]{fontenc} % Use the T1 font encoding
\usepackage{geometry} % Adjust page margins
\usepackage{amsmath, amssymb} % For math symbols and equations
\usepackage{graphicx} % For including images
\usepackage{titlesec} % For customizing section titles
\usepackage[style=authoryear]{biblatex}  % For managing references
\addbibresource{bibfile.bib}
\usepackage{hyperref}
\newcommand{\miscon}[1]{\textbf{#1}}
\newcommand{\surmisedMiscon}[1]{\miscon{#1}$^\ddag$}
\newcommand{\pValue}[0]{\textit{p}\nobreakdash-value}
\newcommand{\rqI}{What are the program-behavior misconceptions that apply to most modern programming languages and present (even) in students with prior programming backgrounds?}
\newcommand{\rqII}{What would be a tutoring system that aims at correcting the misconceptions, draws on cognitive, educational, or psychological concepts, and seems to be effective?}

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{tabularx}   %% For tables with growable column
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\usepackage{cleveref}   %% For smart ref
\usepackage{graphicx}   %% For inserting images
\graphicspath{ {./images/} }  %% configure the graphicx package
\usepackage{multirow}
\usepackage{multicol}
\usepackage{ragged2e}  %% For \raggedright
\usepackage{listings}  %% For typesetting code
\usepackage{enumitem}  %% For noitemsep and topsep
\lstdefinelanguage{smol} {
  alsoletter={ABCDEFGHIJKLMNOPQRSTUVWXYZabcdefghijklmnopqrstuvwxyz-!?*},
  morekeywords={defvar,deffun,lambda,set!,let,let*,letrec,begin,if,cond,else,and,or},
  morecomment=[l]{;},
  morestring=[b]",
}
\lstset{
  basicstyle=\small\ttfamily,
  breaklines=true,
  language=smol
}
%% Custom commands:
%% new terms are introduced with a boldface
%% (the common style is italic, but KC thinks bf is easier to locate)
\newcommand{\newterm}[1]{\textbf{#1}}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Misconceptions about core linguistic concepts like mutable
  variables, mutable compound data, and their interaction with scope
  and higher-order functions seem to be widespread.
  But
  how do we detect
  them, given that experts have blind spots and may not realize the
  myriad ways in which students can misunderstand programs?
  Furthermore, once identified, what can we do to correct them?

  In this proposal, I present a curated list of misconceptions, and an
  instrument to detect them. These are distilled from student work
  over several years and match and extend prior research.  I also
  present an automated, self-guided tutoring system. The tutor builds
  on strategies in the education literature and is explicitly designed
  around identifying and correcting misconceptions.

  I have tested the tutor in multiple settings.
  Our data consistently show that (a) the misconceptions I tackle are
  widespread, and (b) the tutor appears to improve understanding.

  [FILL future work]
\end{abstract}

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

@@

As the related work section (\Cref{s:rel-work}) describes,
multiple researchers, in different
countries and different kinds of post-secondary educational contexts,
have studied how students fare with scope and state. They consistently
find that even advanced students have difficulty with such programs
and even programs simpler than this.

@@

To answer my research questions, I have (a) run a multi-year,
multi-phase study to identify these misunderstandings while trying to
work around the blind spots of experts (and also drawing on prior
work), and (b) constructed the SMoL Tutor, an interactive tutor to
address these misunderstandings. The SMoL Tutor is not a
\emph{programming} tutor; rather, it assumes the user has some basic
facility with programming (i.e., that they are already familiar with
concepts like vectors, mutation, and higher-order functions). It is
built around SMoL's features and their interactions, and draws on
cognitive and educational psychology concepts to expressly identify
and correct misconceptions.

Concretely, I have made the following contributions:
\begin{enumerate}

  \item I provide a collection of brief programs for detecting
        misconceptions about the features of SMoL and their
        interaction. These programs are short and most are readily
        translatable to a wide variety of programming languages that
        share the SMoL characteristics.

  \item I show that multiple populations have problems with these
        programs.

  \item I present a list of curated misconceptions generated
        after multiple rounds of analysis.

  \item I implement these misconceptions as interpreters, which
        find weaknesses in our manual analysis and hold potential for
        generative use in the future.

  \item I present a tutoring system, the SMoL Tutor, that measurably
        corrects these misconceptions.

  \item I present a notional machine, the Stacker, that is used by the
  SMoL Tutor to explain programs and might be useful in itsown.

This document first presents the current results and ends with future
work \& timeline (\cref{s:future-work}).

\paragraph{A Note on Terminology} I use the term
``behavior'' to refer to the meaning of programs in terms of the
answers they produce. A more standard term for this would, of course, be
``semantics''. However, the term ``semantics tutor'' might
mislead some readers into thinking it
teaches people to read or write a formal semantics, e.g., an
introduction to ``Greek'' notation. Because that is not the kind of
tutor I are describing, to avoid confusion, I use the term
``behavior'' instead.

\section{Background: Tutoring Systems and Pedagogic Techniques}
\label{s:background}

There is an extensive body of literature on tutoring systems (\cite{vanlehnBehaviorTutoringSystems2006a} is
a quality survey), and indeed whole conferences are dedicated to
them. I draw on this literature. In particular, it is common in the
literature to talk about a ``two-loop'' architecture \cite{vanlehnBehaviorTutoringSystems2006a} where the outer
loop iterates through ``tasks'' (i.e., educational activities) and the inner loop iterates through UI events within a task. I follow the same
structure in our tutor (\Cref{s:tutor-uiux}).

Many tutoring systems focus on teaching programming
(such as the well-known and heavily studied LISP Tutor \cite{andersonLISPTutor1985}), and in
the process undoubtedly address some program behavior
misconceptions. Our SMoL Tutor differs in a notable way: it does not
try to teach programming per se. Instead, it assumes a basic
programming background and focuses entirely on program behavior misconceptions
and correcting them. I are not aware of a tutoring system (in computer science) that has
this specific design.

@@

@@

To answer this RQ, I need to first define what I mean by ``apply to
most modern programming languages''. As I described in the
Introduction (\Cref{s:intro}), most modern languages share a semantic
core. I have modelled this core as SMoL (\Cref{s:smol}). Because SMoL
represents the semantic core, misconceptions about SMoL presumably
also apply to most modern PLs.

To find misconceptions that ``present (even) in students with prior
programming backgrounds'', I have been collecting data from multiple
populations that very likely have prior experience
(\Cref{s:generality-tutor}). For example, my priliminary results are
build upon data collected in a upper-year programming language course
at Brown. [FILL list the data sources]

To find a reasonably comprehensive collection of misconceptions, I
seek for inputs from students. Most prior works
(\Cref{s:background-misconceptions}) have experts coming up with a
list of potential misconceptions and then filter the potential
misconceptions with student inputs. This approach can't possibly find
misconceptions not considered by experts and hence is necessarily
affected by experts' blind spots. To overcome experts' blind spots, I
analyze a dataset produced by a two-year process to find (a)
student-written programs that tend to trip up students and (b)
incorrect responses to those programs (\Cref{s:gen-prob-quizius}),
using a tool for the purpose (\Cref{s:quizius}). I have been cleaning
up those programs (\Cref{s:smol-quizzes,s:tutor-refine-program-set})
and confirming that these programs are still tricky in the same way
(\Cref{s:misconceptions-quiz,s:misconceptions-tutor}).
\Cref{s:misconceptions-tutor} list misconceptions found with this
process.

I have been creating a tutoring system to answer my RQ2. The tutoring
system collects more student data, which becomes another source of
misconceptions. The tutoring system, which I explain in details when I
talk about RQ2 (\Cref{s:plan-rq2}), includes many tasks that asks
students to predict the result(s) of running a program. I have found
several unanticipated patterns of errors
(\Cref{s:misconceptions-tutor}), which suggest the existence of
unknown misconceptions. The current system do not collect students'
rationale for their answers. So I do not know what are the underlying
misconceptions (although some of the wrong answers are somewhat
self-explanatory). I plan to change the system such that it asks
students' for their explanations when they give a wrong answer. I plan
to eyeball the explanations to find new misconceptions.

To be reasonably specific about misconceptions, I have created a
definitional interpreter for each misconception that I have found. I
plan to do the same things for newly found/confirmed misconceptions.

Eventually, I expect to build a table of misconceptions. Each
misconception comes with two or more programs. For each of these
programs, the wrong result that correspond to the misconception should
be commonly predicted by students from various population.
Furthermore, these students should give similar explanations for all
the wrong answers. For example, I might find a misconception called
\miscon{DefByRef}: when students are asked to predict the result of
\begin{lstlisting}
  (defvar x 12)
  (defvar y x)
  (set! y 0)
  x
  y
\end{lstlisting}
X\% of them responded \lstinline|12 0|; and when asked to predict
\begin{lstlisting}
  (defvar x 12)
  (defvar y x)
  (set! x 0)
  x
  y
\end{lstlisting}
Y\% of them responded \lstinline|0 12|; and these students all
explained something like ``\lstinline|y| is \lstinline|x|''.

@@

To answer this RQ, I have done some literature review on what
pedagogic techniques are helpful (\Cref{s:background}). My current
takeaway is that refutation text, case comparison, and notional
machines are helpful. And I have created a tutoring system (hereafter,
the tutor) (\Cref{s:system-tutor}) that incorporates refutation text
and case comparison (\Cref{s:tutor-uiux}). I am adding notional
machine to the tutor and plan to explore more literature and to
improve the tutor if I find new helpful techniques.

I would like to first explain key aspects of the tutor
(\Cref{s:tutorials,s:interpreting-task}) and then how the tutor
incorporates ideas of refutation text (\Cref{s:refutationt-text}),
case comparsion (\Cref{s:case-comparison}), and notional machines
(\Cref{s:notional-machine}). Finally, I present my plan to evaluate
the effectiveness of the tutor and how evaluation impacts the tutor
design (\Cref{s:evaluation}).

\subsection{Tutorials}%
\label{s:tutorials}

There are many misconceptions to correct. To make the tutoring process
managable, I have design the tutor as a sequence of tutorials.

Inspired by prior research on language levels (\Cref{s:background}),
my sequence of tutorials is ordered, and each later tutorials cover
one or more language constructs (\Cref{t:tutorials}).

@@

\subsection{Interpreting Task}%
\label{s:interpreting-task}

@@

The tutor has been presenting a refutation text when a student chooses
a wrong answer that correspond to known misconception(s). Let's
reconsider the program in \Cref{s:interpreting-task}. If a student
answers \lstinline|0 0|, which suggests they hold the
\miscon{DefByRef} misconception, the tutor responds
\begin{quote}
  \lstinline|y| was bound to \lstinline|12| (i.e., the value of
  \lstinline|x|) rather than to \lstinline|x|. So changing the value
  of \lstinline|y| does not changes the value of \lstinline|x|.
\end{quote}
If a students gave a wrong answer that does not correspond to a
misconception (either by choosing one of the generated option or by
choosing the ``Other'' option), the tutor presents a generic
explanation. For example, if a student answers \lstinline|12 12|, the
tutor responds
\begin{quote}
  The first definition binds \lstinline|x| to \lstinline|12|. The
  second definition binds \lstinline|y| to the value of \lstinline|x|,
  which is \lstinline|12|. The \lstinline|set!| mutates the binding of
  \lstinline|y|, so \lstinline|y| is now bound to \lstinline|0|.
\end{quote}
If a student gave the correct answer, the tutor also presents the
generic explanation.

@@

\section{Proposal Roadmap}
\label{s:roadmap}
\label{s:univ-1-course}

This proposal describes a four-year effort to obtain a quality instrument
to measure misconceptions and to build a tutor to address them.

The first step was a two-year process to generate (a) programs that
tend to trip up students and (b) incorrect responses to those programs
(\Cref{s:gen-prob-quizius}), using a tool for the purpose
(\Cref{s:quizius}). These were then curated (\Cref{s:smol-quizzes}) to
produce an instrument that was tested for one more year
(\Cref{s:misconceptions-quiz}). This underwent one more round of
curation to produce the final instrument~(\Cref{s:tutor-refine-program-set}).

I then present the tutor (\Cref{s:system-tutor}). In particular, we
present the list of misconceptions---grounded in student data---that
are the focus of this project (\Cref{s:misconceptions-tutor}). I also
evaluate the tutor's effectiveness at correcting them
(\Cref{s:effect-tutor}).

All this work is done with students in a ``Principles of Programming
Languages'' class at a selective, private US university. The class has
about 70--75 students per year. It is not required, so students take
it by choice. Virtually all are computer science majors. Most are in
their third or fourth year of tertiary education; about 10\% are
graduate students. All have had at least one semester of imperative
programming, and most have significantly more experience with it. Most
have had close to a semester of functional programming. The student
work described here was required, but students were graded on effort,
not correctness.

Naturally, we should wonder to what extent the demographic affects the
results: we may simply be studying weaknesses at this institution! We
therefore work with two other populations
(\Cref{s:generality-tutor}). In both, we find similar results.

>>>>

% TODO
% - clean up the background sections

\usepackage[switch]{lineno}
\usepackage{xcolor}
\renewcommand\thelinenumber{\textcolor{red}{\arabic{linenumber}}}
\usepackage[utf8]{inputenc} % Use UTF-8 encoding
\usepackage[T1]{fontenc} % Use the T1 font encoding
\usepackage{geometry} % Adjust page margins
\usepackage{amsmath, amssymb} % For math symbols and equations
\usepackage{graphicx} % For including images
\usepackage{titlesec} % For customizing section titles
\usepackage[style=authoryear]{biblatex}  % For managing references
\addbibresource{bibfile.bib}
\usepackage{hyperref}
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{tabularx}   %% For tables with growable column
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\usepackage{cleveref}   %% For smart ref
\usepackage{graphicx}   %% For inserting images
\graphicspath{ {./images/} }  %% configure the graphicx package
\usepackage{multirow}
\usepackage{multicol}
\usepackage{ragged2e}  %% For \raggedright
\usepackage{listings}  %% For typesetting code
\usepackage{enumitem}  %% For noitemsep and topsep
\lstdefinelanguage{smol} {
  alsoletter={ABCDEFGHIJKLMNOPQRSTUVWXYZabcdefghijklmnopqrstuvwxyz-!?*},
  morekeywords={defvar,deffun,lambda,set!,let,let*,letrec,begin,if,cond,else,and,or},
  morecomment=[l]{;},
  morestring=[b]",
}
\lstset{
  basicstyle=\small\ttfamily,
  breaklines=true,
  language=smol
}

\newcommand{\miscon}[1]{\textbf{#1}}
\newcommand{\surmisedMiscon}[1]{\miscon{#1}$^\ddag$}
\newcommand{\newterm}[1]{\textbf{#1}}

%% abbrev. for p-value
\newcommand{\pValue}[0]{\textit{p}\nobreakdash-value}

%% abbrev. for RQs
\newcommand{\rqI}{What are the program-behavior misconceptions that apply to SMoL and present (even) in students with prior programming backgrounds?}
\newcommand{\rqII}{What would be a tutoring system that aims at correcting the misconceptions, draws on cognitive, educational, or psychological concepts, and seems to be effective?}

@@

\begin{abstract}
  Misconceptions about core linguistic concepts like mutable
  variables, mutable compound data, and their interaction with scope
  and higher-order functions seem to be widespread. But how do we
  detect them, given that experts have blind spots and may not realize
  the myriad ways in which students can misunderstand programs?
  Furthermore, once identified, what can we do to correct them?

  I propose a plan for finding misconceptions possibly not anticipated
  by experts, and the design of an automated, self-guided tutoring
  system. The tutor builds on strategies in the cognitive and
  educational literature and is explicitly designed around identifying
  and correcting misconceptions. Preliminary results suggest (a) the
  misconceptions I found are widespread, and (b) the tutor appears to
  improve understanding.
\end{abstract}

\maketitle

@@

As a background section (\Cref{s:background-misconceptions}) describes,
multiple researchers, in different
countries and different kinds of post-secondary educational contexts,
have studied how students fare with scope and state. They consistently
find that even advanced students have difficulty with such programs
and even programs simpler than this.

@@

In the rest of this document, I first define SMoL (\Cref{s:smol}),
then presents literature review of misconceptions
(\Cref{s:background-misconceptions}) and tutoring systems
(\Cref{s:background-tutoring-systems}), then outline my research plans
for the RQs (\Cref{s:plan-rq1,s:plan-rq2}). The remaining sections
detail my current progress.

% To answer my research questions, I have (a) run a multi-year,
% multi-phase study to identify these misunderstandings while trying to
% work around the blind spots of experts (and also drawing on prior
% work), and (b) constructed the SMoL Tutor, an interactive tutor to
% address these misunderstandings. The SMoL Tutor is not a
% \emph{programming} tutor; rather, it assumes the user has some basic
% facility with programming (i.e., that they are already familiar with
% concepts like vectors, mutation, and higher-order functions). It is
% built around SMoL's features and their interactions, and draws on
% cognitive and educational psychology concepts to expressly identify
% and correct misconceptions.

% Concretely, I have made the following contributions:
% \begin{enumerate}

%   \item I provide a collection of brief programs for detecting
%         misconceptions about the features of SMoL and their
%         interaction. These programs are short and most are readily
%         translatable to a wide variety of programming languages that
%         share the SMoL characteristics.

%   \item I show that multiple populations have problems with these
%         programs.

%   \item I present a list of curated misconceptions generated
%         after multiple rounds of analysis.

%   \item I implement these misconceptions as interpreters, which
%         find weaknesses in our manual analysis and hold potential for
%         generative use in the future.

%   \item I present a tutoring system, the SMoL Tutor, that measurably
%         corrects these misconceptions.

%   \item I present a notional machine, the Stacker, that is used by the
%         SMoL Tutor to explain programs and might be useful in itsown.

% \end{enumerate}

% This document first presents the current results and ends with future
% work \& timeline (\cref{s:future-work}).

% \paragraph{A Note on Terminology} I use the term
% ``behavior'' to refer to the meaning of programs in terms of the
% answers they produce. A more standard term for this would, of course, be
% ``semantics''. However, the term ``semantics tutor'' might
% mislead some readers into thinking it
% teaches people to read or write a formal semantics, e.g., an
% introduction to ``Greek'' notation. Because that is not the kind of
% tutor I are describing, to avoid confusion, I use the term
% ``behavior'' instead.

@@

\section{Background: Tutoring Systems}%
\label{s:background-tutoring-systems}

There is an extensive body of literature on tutoring systems
(\cite{vanlehnBehaviorTutoringSystems2006a} is a quality survey), and
indeed whole conferences are dedicated to them. I draw on this
literature. In particular, it is common in the literature to talk
about a ``two-loop'' architecture
\cite{vanlehnBehaviorTutoringSystems2006a} where the outer loop
iterates through ``tasks'' (i.e., educational activities) and the
inner loop iterates through UI events within a task. I follow the same
structure in my tutor (\Cref{s:tutor-uiux}).

Many tutoring systems focus on teaching programming (such as the
well-known and heavily studied LISP Tutor
\cite{andersonLISPTutor1985}), and in the process undoubtedly address
some program behavior misconceptions. My tutor differs in a notable
way: it does not try to teach programming per se. Instead, it assumes
a basic programming background and focuses entirely on program
behavior misconceptions and correcting them. I are not aware of a
tutoring system (in computer science) that has this specific design.

@@

To find misconceptions that ``present (even) in students with prior
programming backgrounds'', I have been collecting data from multiple
populations that very likely have prior experience
(\Cref{s:generality-tutor}). I have the following data sources so far:
\begin{description}
  \item[University 1] students in a ``Principles of Programming
    Languages'' class at Brown University. The class has about 70--75
    students per year. It is not required, so students take it by
    choice. Virtually all are computer science majors. Most are in
    their third or fourth year of tertiary education; about 10\% are
    graduate students. All have had at least one semester of
    imperative programming, and most have significantly more
    experience with it. Most have had close to a semester of
    functional programming. The student work described here was
    required, but students were graded on effort, not correctness.
  \item[University 2] a primarily public university in the US. It is
    one of the largest Hispanic-serving institutions in the country. As
    such, its demographic is extremely different from those whose data
    were used above. The Tutor was used in one course in Spring 2023,
    taken by 12 students. The course is a third-year, programming
    language course. The students are required to have taken two
    introductory programming courses (C++ focused).
  \item[Textbook] an instrument was published on the website of a
    programming languages textbook. Over the course of 8 months,
    several hundreds of people submitted to the instrument. To protect
    privacy, I intentionally do not record demographic information,
    but I conjecture that the population is largely self-learners (who
    are known to use the accompanying book), including some
    professional programmers.
\end{description}

To find a reasonably comprehensive collection of misconceptions, I
seek for inputs from students. Most prior works
(\Cref{s:background-misconceptions}) have experts coming up with a
list of potential misconceptions and then filter the potential
misconceptions with student inputs. This approach can't find
misconceptions not envisioned by experts and hence is hindered by
experts' blind spots. To overcome such bias, I analyze a University~1
dataset produced by a two-year process to find (a) student-written
programs that tend to trip up students and (b) incorrect responses to
those programs (\Cref{s:gen-prob-quizius}), using a tool for the
purpose (\Cref{s:quizius}). I have been cleaning up those programs
(\Cref{s:smol-quizzes,s:tutor-refine-program-set}) and confirming that
these programs are still tricky in the same way
(\Cref{s:misconceptions-quiz,s:misconceptions-tutor}).
\Cref{s:misconceptions-tutor} presents the final list of
misconceptions found with this process.

I have another source of misconceptions. I have been creating a tutor
to answer my RQ2. The tutor, which I explain in details when I talk
about RQ2 (\Cref{s:plan-rq2}), includes many tasks that asks students
to predict the result(s) of running a program. I have found several
unanticipated patterns of errors (\Cref{s:misconceptions-tutor}),
which suggest the existence of unknown misconceptions. The tutor is
not collecting students' rationale for their answers. So I do not know
what are the underlying misconceptions (although some of the wrong
answers are somewhat self-explanatory). I plan to change the tutor
such that it asks students' for their explanations when they give a
wrong answer. I plan to eyeball the explanations to find new
misconceptions and to further confirm that anticipated wrong answers
do represent the expected misconceptions.

To be reasonably specific about misconceptions, I have created a
definitional interpreter for each misconception that I have found. I
plan to do the same things for any new misconceptions.

Eventually, I expect to build a table of misconceptions. Each
misconception comes with multiple programs. For each of these
programs, the wrong result that correspond to the misconception should
be commonly predicted by students from various population.
Furthermore, these students should give similar explanations for all
the wrong answers. For example, I might find a misconception called
\miscon{DefByRef}: when students are asked to predict the result of
\begin{lstlisting}
  (defvar x 12)
  (defvar y x)
  (set! y 0)
  x
  y
\end{lstlisting}
X\% of them responded \lstinline|12 0|; and when asked to predict
\begin{lstlisting}
  (defvar x 12)
  (defvar y x)
  (set! x 0)
  x
  y
\end{lstlisting}
Y\% of them responded \lstinline|0 12|; and these students all
explained something like ``\lstinline|y| is \lstinline|x|''.

@@

To answer this RQ, I have done some literature review on what
pedagogic techniques are helpful (\Cref{s:pedagogic-techniques}). My
current takeaway is that refutation text, case comparison, notional
machines, and language levels are helpful.

I have created a tutor (\Cref{s:system-tutor}) that incorporates all
these ideas (\Cref{s:tutor-uiux}) and have collected data from all
populations. I plan to explore more literature and to improve the
tutor if I find new helpful techniques.

I would like to first explain key aspects of the tutor
(\Cref{s:tutorials,s:interpreting-tasks}) and then my plan to
incorporate ideas of refutation text (\Cref{s:refutationt-text}), case
comparsion (\Cref{s:case-comparison}), and notional machines
(\Cref{s:notional-machine}). Finally, I present my plan to evaluate
the effectiveness of the tutor and how evaluation impacts the tutor
design (\Cref{s:evaluation}).

\subsection{Tutorials and Language Levels}%
\label{s:tutorials}

There are many misconceptions to correct. To make the tutoring process
managable, I have design the tutor as a sequence of tutorials.
Inspired by prior research on language levels
(\Cref{s:pedagogic-techniques}), my sequence of tutorials is ordered,
and each later tutorials cover one or more language constructs
(\Cref{t:tutorials}).

@@

\subsection{Interpreting Tasks}%
\label{s:interpreting-tasks}

@@

The tutor has been presenting a refutation text when a student chooses
a wrong answer that correspond to known misconception(s). Let's
reconsider the program in \Cref{s:interpreting-tasks}. If a student
answers \lstinline|0 0|, which suggests they hold the
\miscon{DefByRef} misconception, the tutor responds
\begin{quote}
  \lstinline|y| was bound to \lstinline|12| (i.e., the value of
  \lstinline|x|) rather than to \lstinline|x|. So changing the value
  of \lstinline|y| does not changes the value of \lstinline|x|.
\end{quote}
If a students gave a wrong answer that does not correspond to a
misconception (either by choosing one of the generated option or by
choosing the ``Other'' option), the tutor presents a generic
explanation. For example, if a student answers \lstinline|12 12|, the
tutor responds
\begin{quote}
  The first definition binds \lstinline|x| to \lstinline|12|. The
  second definition binds \lstinline|y| to the value of \lstinline|x|,
  which is \lstinline|12|. The \lstinline|set!| mutates the binding of
  \lstinline|y|, so \lstinline|y| is now bound to \lstinline|0|.
\end{quote}
If a student gave the correct answer, the tutor also presents the
generic explanation.

@@

\section{What Pedagogic Techniques are Effective?}%
\label{s:pedagogic-techniques}
